\cvsection{Work Experience}

\begin{cventries}

	\cventry
	{Systems Engineer}
	{Stack Overflow / Stack Exchange}
	{Remote}
	{Jan 2021 - Present}
	{
		\begin{cvitems}
		\item {Configured Azure production and development environments for IT using Atlantis automation.}
		\item {Wrote tool to securely provide credentials from Azure Key Vault. (https://github.com/Aechrok/envy)}
		\item {Wrote tool that takes in webhooks and twilio SMS messages, formats, and then sends to other tools.}
		\item {Wrote many libraries for tools to handle day-to-day API use. (Workspace One, Azure Key Vault, SendSafely, etc.)}
		\item {Planned and configured the transition to Workspace ONE using Okta, Apple DEP, and Windows Autopilot.}
		\item {Massively integrated Okta into all faucets of the company.}
		\item {2021 Hardware Refresh. Deployed new server hardware and transitioned the Stack Exchange network live.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{Linux Systems Administrator}
	{Vultr.com / Constant, LLC}
	{Remote}
	{Feb 2018 - Jan 2021}
	{
		\begin{cvitems}
		\item {Worked with Tencent/Activision to monitor, support, and buildout the core infrastructure for Call of Duty Mobile for deployment on VULTR platform globally. Included weekly meetings with all three companies teams via teleconference and using Activision's JIRA for project tickets and GIT for version control.}
		\item {Internal Active Directory Domain Admin, PBX Admin (Using 3CX Software), Icinga/Nagios Admin}
		\item {PBX Internal Admin (Using 3CX Software), Icinga/Nagios Admin}
		\item {Support for customer-facing systems, pro-active customer service, and support infrastructure of 8,000 servers in a globally distributed, multi-homed topology for Choopa, Constant, ReliableServers, Unmetered Servers, Gameservers, as well as VULTR.}
		\item {Provided incident response for vulnerabilities such as Meltdown/Spectre, etc.}
		\item {Senior on-shift for escalations.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{Field Service Technician II}
	{ConvexSERV Technology Solutions, LLC}
	{Forked River, NJ}
	{Jun 2017 - Feb 2018}
	{
		\begin{cvitems}
		\item {Domain and network administrator.}
		\item {Provide Level II technical support. Configure and troubleshoot VPNs and remote connections.}
		\end{cvitems}
	}

	%---------------------------------------------------------------------------

	\cventry
	{Infantry Team Leader}
	{82nd Airborne Division, U.S. Army}
	{Fort Bragg, NC}
	{July 2008 - Feb 2012}
	{
		\begin{cvitems}
		\item {Commanded a 5-man fire team during a 1-year combat deployment with the 82nd Airborne Division as an Infantryman.}
		\item {Service-Connected Veteran.}
		\end{cvitems}
	}

\end{cventries}
